Adaptive Resolution Simulation in Equilibrium and Beyond

### 2015-02-21 writeDown/pub.epj/paper.tex
change email
revise the paper according to the referees

%
\begin{document}
%
\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Zuse Institute Berlin (ZIB), Germany
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
\abstract{ In this paper,
  we investigate the equilibrium statistical properties of both the force and potential interpolations of
  adaptive resolution simulation (AdResS) under the theoretical framework of
  grand-canonical like AdResS (GC-AdResS).
  The thermodynamic relations between the higher and lower resolutions are
  derived by considering the absence of fundamental conservation laws in mechanics for both branches of AdResS.
  % we discuss the necessary conditions for
  % accurate adaptive resolution simulation (AdResS) in equilibrium.
  % The statistical and thermodynamical properties of two AdResS
  % branches, i.e.~the force and the potential interpolations, are
  % discussed and compared in parallel.
  In order to investigate the applicability of AdResS method in studying the properties
  beyond the equilibrium, we demonstrate the accuracy of AdResS in computing the dynamical properties in
  two numerical examples: The velocity auto-correlation of pure water
  and the conformational relaxation of alanine dipeptide dissolved in water.
  Theoretical and technical open questions of the AdResS method are discussed in the end of the paper.
} %end of abstract
%
\maketitle
%

@@

The time evolution of a classical molecular systems
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied in the same system~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaks the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while break the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties, cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, not equilibrium averages.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
and to the best of our knowledge, there is no theoretical answers on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method, e.g.~the Reaction-Field method.
} being treated
by the cut-off method, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the accumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

@@

In order to consider the accuracy of the AdResS from statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is same as the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem is
subject to the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS is also subject to the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

The thermodynamic limit is taken in the sense that both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much smaller than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the volumes of the
three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservoir for the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by. In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponding to the atomistic region samples the
grand-canonical ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonical ensemble in the thermodynamic limit? More
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
the desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, and $\mh^\AT$ is the \emph{atomistic}
Hamiltonian.
% defined in the the subregion of the reference system that
% corresponds to the atomistic region of the AdResS system.

@@

\subsection{The accuracy of the configurational probability density}
The configurational probability density~\eqref{eqn:dist-1-0} is further split as
\begin{align}\label{eqn:conf-split}
  p(\vect x_\AT \vert N_\AT) =
  \sum_{N_\HY} \int {d}\vect x_\HY\,
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)\cdot
  p(\vect x_\HY, N_\HY\vert N_\AT)  
\end{align}
The first probability density in the integral is the probability density
of atomistic DOFs conditioned on the number of atomistic molecules and all
hybrid DOFs.
It can be shown that if
(1) All interactions in the system are cut-offed;
(2) The atomistic region interacts with the hybrid region only in an atomistic way;
(3) The system is short-range correlated, and the correlation between the atomistic
and the coarse-grained regions is negligible, then the probability density $p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)$
is approximated by
\begin{align}\label{eqn:dist-conf-0}
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)
  \propto
  \exp\Big\{-\beta \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY) \Big\},
\end{align}
where 
\begin{align}
  \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY)
  =
  \sum_{i=1}^{N_\AT}\frac12 m_i\vect v_i^2 +
  \sum_{i,j=1}^{N_\AT} \frac12 V^\AT(\vect r_{ij}) +
  \sum_{i=1}^{N_\AT}\sum_{j=N_\AT+1}^{N_\AT + N_\HY} V^\AT(\vect r_{ij})
\end{align}
is the atomistic Hamiltonian with parameters $\vect x_\HY, N_\HY$. It
should be noted that the probability density~\eqref{eqn:dist-conf-0}
is identical to that of the reference system.
% with a subregion that
% corresponds to the hybrid region.
The probability density and local Hamiltonian
can be written down for the coarse-grained region analogically.

@@

% In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
% in sampling the equilibrium ensemble.
In principle, all quantities that
can be written down in terms of equilibrium ensemble averages should
be computed with high accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
However, under this framework one has little knowledge regarding the quantities
that are not ensemble averages.
For example, the non-equilibrium response of the system
with respect to an external perturbation, which is 
either computed by brute force non-equilibrium simulations~\cite{wang2014exploring}, or by
equilibrium time-correlation function via the Green-Kubo
relation~\cite{green1954markoff,kubo1957statistical} if the perturbation is small. The
time-correlation function, although measured in equilibrium
simulations, depends on how the dynamics
of the system is implemented.
The quantities of this type are called \emph{dynamical properties} of the system.
In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
however, due to the truncation error in computer simulations, it
is technically difficult to conserve the energy in very long MD simulations.
To this end thermostats are sometimes coupled to keep the system at desired thermodynamic
state.
It is worth noting that the thermostats are designed to sample equilibrium distributions, and 
disturb the Hamiltonian dynamics in an artificial way.
Therefore, when applying the thermostats
in computing the dynamical properties, the potential artifacts
should be checked carefully.
In the context of AdResS, we propose an alternative way of thermostating
the system, the local thermostat method~\cite{wang2014exploring},
which is proved to be free of the artifacts in computing the dynamical properties, in the following section.

@@

The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
used as a testing case for evaluating the new computational method in simulating 
biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
We investigate a system composed of
7235 TIP3P water molecules, and
one alanine dipeptide described by the CHARMM27 force field~\cite{foloppe2000all} with
grid-based energy correction map (CMAP)~\cite{mackerell2004extending}. 
The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
The rest of the system is treated coarse-grainly by the WCA interaction.
The dynamical region  is
also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
It has been proved that the conformational dynamics of alanine dipeptide is not sensitive to the size of
the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
In this case, part of the hybrid region is not thermostated, so
when using force interpolation, the extra energy production might not be effectively equilibriated.
To this end, we only investigate the potential interpolation. The corresponding
thermodynamic force is iteratively computed by
Eq.~\eqref{eqn:tfi}.
The electrostatic interaction is computed by the Reaction-Field method with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
are cut-offed at 1.0~nm.

@@

>>>>

%
\begin{document}
%
\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{wang\_han@iapcm.ac.cn}}, Animesh Agarwal\inst{3}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Zuse Institute Berlin (ZIB), Germany
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
\abstract{ In this paper,
  we investigate the equilibrium statistical properties of both the force and potential interpolations of
  adaptive resolution simulation (AdResS) under the theoretical framework of
  grand-canonical like AdResS (GC-AdResS).
  The thermodynamic relations between the higher and lower resolutions are
  derived by considering the absence of fundamental conservation laws in mechanics for both branches of AdResS.
  % we discuss the necessary conditions for
  % accurate adaptive resolution simulation (AdResS) in equilibrium.
  % The statistical and thermodynamical properties of two AdResS
  % branches, i.e.~the force and the potential interpolations, are
  % discussed and compared in parallel.
  In order to investigate the applicability of AdResS method in studying the properties
  beyond the equilibrium, we demonstrate the accuracy of AdResS in computing the dynamical properties in
  two numerical examples: The velocity auto-correlation of pure water
  and the conformational relaxation of alanine dipeptide dissolved in water.
  Theoretical and technical open questions of the AdResS method are discussed in the end of the paper.
} %end of abstract
%
\maketitle
%

@@

The time evolution of a classical molecular systems
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied in the same system~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaks the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while break the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
very high accuray in equilibrium properties such as the radial distribution function, three-body correlation and chemical potential~\cite{wang2013grand}.}
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties,
\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
% cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation\footnote{
  \recheck{
  The velocity auto-correlation
  % is the ensemble average
  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
  It should be noted that
  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
  therefore, it is a dynamical property. }}.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, dynamical properties.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
and to the best of our knowledge, there is no theoretical answers on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{The general cut-off method is used
    in AdResS MD simulations.  The details of the cut-off method can be find in, e.g., Ref.~\cite{frenkel2001understanding}}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\footnote{
\recheck{
  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the accumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

@@

In order to consider the accuracy of the AdResS from statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is same as the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

The thermodynamic limit is taken in the sense that both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much smaller than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the volumes of the
three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservoir for the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by. In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponding to the atomistic region samples the
grand-canonical ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonical ensemble in the thermodynamic limit? More
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
the desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, $\mh^\AT$ is the \emph{atomistic}
Hamiltonian, \recheck{and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
% defined in the the subregion of the reference system that
% corresponds to the atomistic region of the AdResS system.

@@

\subsection{The accuracy of the configurational probability density}
The configurational probability density~\eqref{eqn:dist-1-0} is further split as
\begin{align}\label{eqn:conf-split}
  p(\vect x_\AT \vert N_\AT) =
  \sum_{N_\HY} \int {d}\vect x_\HY\,
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)\cdot
  p(\vect x_\HY, N_\HY\vert N_\AT)  
\end{align}
The first probability density in the integral is the probability density
of atomistic DOFs conditioned on the number of atomistic molecules and all
hybrid DOFs.
It can be shown that if
(1) All interactions in the system are cut-off;
(2) The atomistic region interacts with the hybrid region only in an atomistic way;
(3) The system is short-range correlated, and the correlation between the atomistic
and the coarse-grained regions is negligible, then the probability density $p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)$
is approximated by
\begin{align}\label{eqn:dist-conf-0}
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)
  \propto
  \exp\Big\{-\beta \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY) \Big\},
\end{align}
where 
\begin{align}
  \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY)
  =
  \sum_{i=1}^{N_\AT}\frac12 m_i\vect v_i^2 +
  \sum_{i,j=1}^{N_\AT} \frac12 V^\AT(\vect r_{ij}) +
  \sum_{i=1}^{N_\AT}\sum_{j=N_\AT+1}^{N_\AT + N_\HY} V^\AT(\vect r_{ij})
\end{align}
is the atomistic Hamiltonian with parameters $\vect x_\HY, N_\HY$. It
should be noted that the probability density~\eqref{eqn:dist-conf-0}
is identical to that of the reference system.
% with a subregion that
% corresponds to the hybrid region.
The probability density and local Hamiltonian
can be written down for the coarse-grained region analogically.

@@

% In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
% in sampling the equilibrium ensemble.
In principle, all quantities that
can be written down in terms of equilibrium ensemble averages should
be computed with high accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
However, under this framework one has little knowledge regarding the quantities
that are \recheck{beyond} ensemble averages.
For example, the non-equilibrium response of the system
with respect to an external perturbation, which is 
either computed by brute force non-equilibrium simulations~\cite{wang2014exploring}, or by
equilibrium time-correlation function via the Green-Kubo
relation~\cite{green1954markoff,kubo1957statistical} if the perturbation is small. The
time-correlation function, although measured in equilibrium
simulations, depends on how the dynamics
of the system is implemented.
The quantities of this type are called \emph{dynamical properties} of the system.
In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
however, due to the truncation error in computer simulations, it
is technically difficult to conserve the energy in very long MD simulations.
To this end thermostats are sometimes coupled to keep the system at desired thermodynamic
state.
It is worth noting that the thermostats are designed to sample equilibrium distributions, and 
disturb the Hamiltonian dynamics in an artificial way.
Therefore, when applying the thermostats
in computing the dynamical properties, the potential artifacts
should be checked carefully.
In the context of AdResS, we propose an alternative way of thermostating
the system, the local thermostat method~\cite{wang2014exploring},
which is proved to be free of the artifacts in computing the dynamical properties, in the following section.

@@

The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
used as a testing case for evaluating the new computational method in simulating 
biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
We investigate a system composed of
7235 TIP3P water molecules, and
one alanine dipeptide described by the CHARMM27 force field~\cite{foloppe2000all} with
grid-based energy correction map (CMAP)~\cite{mackerell2004extending}. 
The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
The rest of the system is treated coarse-grainly by the WCA interaction.
The dynamical region  is
also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
It has been proved that the conformational dynamics of alanine dipeptide is not sensitive to the size of
the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
In this case, part of the hybrid region is not thermostated, so
when using force interpolation, the extra energy production might not be effectively equilibriated.
To this end, we only investigate the potential interpolation. The corresponding
thermodynamic force is iteratively computed by
Eq.~\eqref{eqn:tfi}.
The electrostatic interaction is computed by the Reaction-Field method with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
are cut-off at 1.0~nm.

@@

\section*{Acknowledgments}
The computation of this work was performed at the North-German Supercomputing Alliance (HLRN) under project bec00100. The authors are grateful for this support.
HW would like to acknowledge the finial support from National High Technology Research and Development Program of China under Grant No.~2015AA011201.
